### 2020-12-03 AISTATS2021_Author_Response_Pack/aistats2021_author_response.tex
edit
add

	\textbf{The gap between the theory and experiment in Fig 2.b?} Thanks to R2 and R3 for pointing out this gap.
	We have improved our result so that the theory matches experiment in Fig 2.b (see Figure \ref{fig_update} for the updated result).
	DESCRIBE THE IDEA.

	\textbf{Can any of the results in Section 3 be obtained from a straightforward application of a generalized MP theorem?}
	Thanks for raising this question. R3 is correct that the variance equation in Corollary 3.3 can be obtained from the MP law.
	However, to the best of our knowledge, the bias equation in Corollary 3.3 and Example 3.4 cannot be obtained from the MP law.
	ADD COMMENT TO THAT PAPER.

>>>>

	\textbf{The gap between the theory and experiment in Fig 2.b?} Thanks to R2 and R3 for pointing out this gap.
	We have improved our result so that the theory matches experiment in Fig 2.b (see Figure \ref{fig_update} for the updated result).
	For the new results, we use some delicate free probability techniques to obtain an exact asymptotic limit of the bias term {\color{red}(I am not sure what details you need here)}. %DESCRIBE THE IDEA.

	\textbf{Can any of the results in Section 3 be obtained from a straightforward application of a generalized MP theorem?}
	Thanks for raising this question. R3 is correct that the variance equation in Corollary 3.3 can be obtained from the MP law.
	However, to the best of our knowledge, the bias equation in Corollary 3.3 and Example 3.4 cannot be obtained from the MP law.
	Regarding the paper Ledoit and P{\'e}ch{\'e} (2011) mentioned by R2, the authors deal with a single sample covariance matrix $X^\top X$, where the row vectors of $X$ have the same population covariance matrix. This case cannot be reduced to our case with two sample covariance matrices $X_1^\top X_1$ and $X_2^\top X_2$ that have different population covariance matrices. In particular, if we stack the rows of $X_1$ and $X_2$ into one random matrix $X$, then the row vectors of $X$ have different covariance matrices. Moreover, in order to get the best convergence rates, the method in  Ledoit and P{\'e}ch{\'e} (2011) is not sufficient, and some new techniques in random matrix theory are needed.
